Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2011-11-03 Multiresolution_framework/ltx/manuscript.tex
edits to stopping criteria

 where $\epsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norms  of the successive estimates of $\mathbf{A} $ matrices which is defined by

@@

  \parallel \mathbf{A} \parallel_{F}=\sqrt{\mathrm{tr} (\mathbf A^{\top}\mathbf A)}

>>>>

 where $\epsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norms  of the successive estimates of $\mathbf{A} $ matrices which is defined by \cite{Meyer2000}

@@

  \parallel \mathbf{A} \parallel_{F}=\sqrt{\sum_{i,j=1}^{n_x}\mid a_{i,j} \mid^2}=\sqrt{\mathrm{tr} (\mathbf A^{\top}\mathbf A)}
